PK object batch mode trial

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Finished coef and predict method trials

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch

@@

my_pk <- do_fit(my_pk)
```

Batch mode works now I need to write a function that recapitulates `coef()` method

@@

my_coefs_test <- my_pk$fit |>
  ungroup() |>
  tidyr::unnest(cols = fit) |>
  tidyr::unite(sigma, starts_with("sigma_"),
        na.rm = TRUE) |>
  group_split(method)

my_coef <- function(obj,
                    data_group = NULL,
                    ...) {
  # Check fit status
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)

@@

  # Assign data groups to variable
  if (is.null(data_group)) data_group <- obj$data_group

  fit_coef <- obj$fit |>
    dplyr::ungroup() |>
    tidyr::unnest(cols = fit) |>
    tidyr::unite(sigma, starts_with("sigma_"),
                 na.rm = TRUE)# |>
    # dplyr::group_split(method)

  # method_names <- purrr::map(fit_coef,
  #     \(x) unique(x$method)) |>
  #   unlist()
  # 
  # names(fit_coef) <- method_names

  return(fit_coef)
}

my_coefs <- my_coef(my_pk)

@@

my_predict <- function(obj,
                       newdata = NULL,
                       type = "conc",
                       exclude = TRUE,
                       use_scale_conc = FALSE) {
    # Check fit status
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)

  if (is.null(newdata)) newdata <- obj$data
  newdata_ok <- check_newdata(newdata = newdata,
                              olddata = obj$data,
                              req_vars = c("Time",
                                           "Time.Units",
                                           "Dose",
                                           "Route",
                                           "Media"),
                              exclude = exclude)

    #scale time if needed
  if (!("Time_trans" %in% names(newdata))){
  newdata$Time_trans <- convert_time(x = newdata$Time,
                                     from = newdata$Time.Units,
                                     to = obj$scales$time$new_units)
  }

@@

}

>>>>

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
tidyverse_conflicts()
```

@@

my_pk <- do_fit(my_pk)

Batch mode works, now I need to write a function that recapitulates `coef()` method

@@

const_pars <- subset(my_pk$prefit$par_DF,
       optimize_param %in% FALSE &
         use_param %in% TRUE) %>% dplyr::select(model, Chemical, Species,
                                         param_name, start) 
const_pars <- const_pars %>%
  pivot_wider(names_from = param_name,
              values_from = start)

my_fit_test <- my_pk$fit %>% unnest(cols = fit) %>%
  group_by(model, method, Chemical, Species) %>%
  dplyr::select(starts_with("sigma_"),
                any_of(sapply(my_pk$stat_model, `[[`, "params") %>%
                         unlist() %>%
                         unique())) # need Rblood2plasma

left_join(my_fit_test, const_pars)

# New possible coef function!!
my_coef <- function(obj,
                    data_group = NULL,
                    ...) {
  # Check fit status
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)

@@

  const_pars <- subset(obj$prefit$par_DF,
                       optimize_param %in% FALSE &
                         use_param %in% TRUE) %>% dplyr::select(model,
                                                                !!!obj$data_group,
                                                                param_name,
                                                                start) 
  const_pars <- const_pars %>%
    pivot_wider(names_from = param_name,
                values_from = start)

  possible_model_params <- sapply(obj$stat_model, `[[`, "params") %>%
    unlist() %>%
    unique()

  coefs <- obj$fit %>% unnest(cols = fit) %>%
  group_by(model, method, !!!obj$data_group) %>%
  dplyr::select(starts_with("sigma_"),
                any_of(possible_model_params)) %>%
    unite(starts_with("sigma_"),
          col = "sigma",
          sep = "",
          na.rm = TRUE)

  coefs <- left_join(coefs, const_pars)

  coefs_tidy <- coefs %>%
  nest(coefs_tibble = any_of(possible_model_params)) %>%
  mutate(coefs_vector = map(coefs_tibble,
                      .f = \(x){
                        as.data.frame(x %>%
                                    dplyr::select(!where(is.na))) %>% 
                          unlist()
                      })) %>%
    unnest(coefs_tibble)
  return(coefs_tidy)
}

my_coefs <- my_coef(obj = my_pk)

@@

my_predict <- function(obj,
                       newdata = NULL,
                       model = NULL,
                       method = NULL,
                       type = "conc",
                       exclude = TRUE,
                       use_scale_conc = FALSE,
                       ...){

  #ensure that the model has been fitted
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)
  if(!(check %in% TRUE)){
    stop(attr(check, "msg"))
  }

  if(is.null(model)) model <- names(obj$stat_model)
  if(is.null(method)) method <- obj$settings_optimx$method

  method_ok <- check_method(obj = obj, method = method)
  model_ok <- check_model(obj = obj, model = model)

  coefs <- my_coef(obj = obj) %>%
    dplyr::filter(model %in% model,
                  method %in% method)

  if(is.null(newdata)) newdata <- obj$data

  newdata_ok <- check_newdata(newdata = newdata,
                              olddata = obj$data,
                              req_vars = c("Time",
                                           "Time.Units",
                                           "Dose",
                                           "Route",
                                           "Media"),
                              exclude = exclude)

  #scale time if needed
  if(!("Time_trans" %in% names(newdata))){
    newdata$Time_trans <- convert_time(x = newdata$Time,
                                       from = newdata$Time.Units,
                                       to = obj$scales$time$new_units)
  }

@@

  req_vars <- c("Time",
                "Time.Units",
                "Dose",
                "Route",
                "Media",
                "Value",
                "Value.Units")

  trans_vars <- c("Time_trans",
                  "Time_trans.Units",
                  "Conc_trans",
                  "Conc_trans.Units")

  newdata <- newdata %>%
    dplyr::select(!!!obj$data_group,
                  all_of(req_vars),
                  any_of(trans_vars)) %>%
    group_by(!!!obj$data_group,
             Route, Media) %>%
    nest(.key = "observations")

  newdata <- left_join(coefs, newdata,
                       relationship = "many-to-many")
  # From here, trying to call map within mutate to add the prediction column by
  # calling the appropriate model function and feeding it the parameters in coefs_vector

  newdata <- newdata %>%
    dplyr::group_by(Route, Media,
                    .add = TRUE) %>%
    mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
    reframe(predictions = 
              map(observations,
                  .f = \(x) {
                    x %>%
                      group_by(Time_trans) %>%
                      mutate(Conc_est = sapply(coefs_vector,
                                               FUN = model_fun,
                                               time = Time_trans,
                                               dose = ifelse(obj$scales$conc$dose_norm,
                                                             1, Dose),
                                               route = Route,
                                               medium = Media,
                                               simplify = TRUE,
                                               USE.NAMES = TRUE))
                              })) %>%
    unnest(predictions)

  return(newdata) 
}

my_pred <- my_predict(my_pk, use_scale_conc = TRUE)

my_pred %>%
  filter(model == "model_flat",
         Route == "iv",
         Species == "hamster",
         method == "L-BFGS-B") %>%
  View()
